Figures

### 2016-06-25 figures/figures.rmd
figures

d_littleR_m <- melt(vir_matS,value.name="Mean.VL")
shirreff_df_m <- subset(res_sum_df,run==1,select=c(run,Time, Mean.VL))
shirreff_df_m$run <- "Shirreff"
df_tot <- rbind(shirreff_df_m,d_littleR_m)
tlab <- "time (years)"
g1 <- ggplot(df_tot,aes(x=Time,y=Mean.VL,colour=run))+
    geom_line()+labs(x=tlab,y=expression(mean~virulence~(log[10]~SPVL)))+
    theme(legend.position=c(0.75,0.25))
###
dimnames(vir_matS2) <- list(Time=tvec,
               run=c("10^{-3}", "10^{-4}", "10^{-5}"))
g2 <- g1 %+% melt(vir_matS2,id.var="Time",value.name="Mean.VL") +
	labs(y = "")
###
dimnames(vir_matS3) <- list(Time=tvec,
                            run=c("2.5", "3", "3.5"))

@@

gg_virtraj <- ggplot(ss,
                     aes(tvec,mean,ymin=lwr,ymax=upr))+
	geom_line(aes(colour=model,linetype=model),lwd=1)+
	geom_ribbon(aes(fill = model), alpha=0.3)+
	labs(x="time (years)",y=expression(mean~virulence~(log[10]~SPVL))) +
	theme(axis.title.y = element_text(margin = margin(0,10,0,0)),
		axis.title.x = element_text(margin = margin(10,0,0,0))) +
	facet_wrap(~model, nrow = 2) +
	zero_margin

@@

gg_betatraj <- ggplot(ss2,
                     aes(tvec,mean,ymin=lwr,ymax=upr))+
	geom_line(aes(colour=model,linetype=model),lwd=1)+
	geom_ribbon(aes(fill = model), alpha=0.3)+
	labs(x="time (years)",y=expression(mean~transmission~rate~during~asymptomatic~stage)) +
	theme(axis.title.y = element_text(margin = margin(0,10,0,0)),
		axis.title.x = element_text(margin = margin(10,0,0,0))) +
	facet_wrap(~model, nrow = 2) +
	zero_margin

@@

gg_durtraj <- ggplot(ss3,
                     aes(tvec,mean,ymin=lwr,ymax=upr))+
	geom_line(aes(colour=model,linetype=model),lwd=1)+
	geom_ribbon(aes(fill = model), alpha=0.3)+
	labs(x="time (years)",y=expression(mean~duration~of~asymptomatic~stage)) +
	theme(axis.title.y = element_text(margin = margin(0,10,0,0)),
		axis.title.x = element_text(margin = margin(10,0,0,0))) +
	facet_wrap(~model, nrow = 2) +
	zero_margin

@@

gg_univ <- ggplot(mLw,aes(value,model,fill=model))+
	geom_violinh(width=1)+
	facet_wrap(~variable,scale="free_x")+
	guides(fill=guide_legend(reverse=TRUE))+
	labs(y="")+
	geom_point(data=data.frame(model="random",variable="equilibrium virulence",
                               value=rval),pch=22,size=3,show.legend=FALSE) +
	zero_x_margin
print(gg_univ)

@@

sL <- transform(sum_list[["sum_mat"]],rel_peak=peak_vir/eq_vir)
sL$model <- factor(sL$model, c("random","pairform+epc", "pairform", "instswitch+epc","instswitch" , "implicit"))

@@

gg_univ.epi <- ggplot(mLw.epi,aes(value,model,fill=model))+
	geom_violinh(width=1)+
	facet_wrap(~variable,scale="free_x")+
	guides(fill=guide_legend(reverse=TRUE))+
	labs(y="")+
	geom_point(data=data.frame(model="random",variable=c("Equilbrium asymptomatic transmission rate",
																											 "Equilibrium duration of asymptomatic stage"),
                               value=c(rval.epi.t, rval.epi.d)),pch=22,size=3,show.legend=FALSE) +
	zero_x_margin
print(gg_univ.epi)

@@

```{r sumtab,as.is=TRUE}
rq <- function(x,q,digits=3) {
    round(quantile(x,q),digits)
}
mLtab <- mL.epi %>% group_by(model,variable) %>%
    summarise(lwr=rq(value,0.025),
              med=rq(value,0.5),
              upr=rq(value,0.975)) %>%
    mutate(variable=abbreviate(variable,30)) %>%
    ungroup() %>%
    arrange(variable,model)
kable(mLtab)
```
```{r sumvals,echo=FALSE}
ff <- function(model,variable,r=3) {
    mm <- mLtab[mLtab$model==model & mLtab$variable==variable,3:5]
    round(unlist(mm),r)
}
mindur_random <- ff("random","peak_dur",1)
mindur_pfepc <-  ff("pairform+epc","peak_dur",1)
mindur_implicit  <- ff("implicit","peak_dur",1)
maxt_random <- ff("random","peak_t",2)
maxt_pfepc <- ff("pairform+epc","peak_t",2)
maxt_implicit  <- ff("implicit","peak_t",2)
save(list=ls(pattern="^(maxt|mindur)"),file="../ms/maxminstats.RData")
```
```{r fig4_func, echo = FALSE}
trim_gg <- function(gg,hack_spaces=TRUE) {
    n <- gg$nrow
    gg$nrow <- gg$ncol <- n-1
    v <- 1:n^2
    gg$plots <- gg$plots[v>n & v%%n!=0]
    gg$xAxisLabels <- gg$xAxisLabels[-n]
    gg$yAxisLabels <- gg$yAxisLabels[-1]
    ## ggpairs tries to parse labels, so this fails if they
    ## have spaces in them ... maybe there's a better way?
    if (hack_spaces) {
        gg$xAxisLabels <- gsub("_"," ",gg$xAxisLabels)
        gg$yAxisLabels <- gsub("_"," ",gg$yAxisLabels)
    }
    return(gg)
}

>>>>

d_littleR_m <- melt(vir_matS,value.name="Mean.VL")
shirreff_df_m <- subset(res_sum_df,run==1,select=c(run,Time, Mean.VL))
shirreff_df_m$run <- "Shirreff"
df_tot <- rbind(shirreff_df_m,d_littleR_m)
tlab <- "time (years)"
g1 <- ggplot(df_tot,aes(x=Time,y=Mean.VL,colour=run))+
    geom_line()+labs(x=tlab,y=expression(population~mean~set-point~viral~load~(log[10])))+
    theme(legend.position=c(0.75,0.25))
###
dimnames(vir_matS2) <- list(Time=tvec,
               run=c("10^{-3}", "10^{-4}", "10^{-5}"))
g2 <- g1 %+% melt(vir_matS2,id.var="Time",value.name="Mean.VL") +
	labs(y = "")
###
dimnames(vir_matS3) <- list(Time=tvec,
                            run=c("2.5", "3", "3.5"))

@@

gg_virtraj <- ggplot(ss,
                     aes(tvec,mean,ymin=lwr,ymax=upr))+
	geom_line(aes(colour=model,linetype=model),lwd=1)+
	geom_ribbon(aes(fill = model), alpha=0.3)+
	labs(x="time (years)",y=expression(population~mean~set-point~viral~load~(log[10]))) +
	theme(axis.title.y = element_text(margin = margin(0,10,0,0)),
		axis.title.x = element_text(margin = margin(10,0,0,0)),
		legend.position = "none") +
	facet_wrap(~model, nrow = 2) +
	zero_margin

@@

gg_betatraj <- ggplot(ss2,
                     aes(tvec,mean,ymin=lwr,ymax=upr))+
	geom_line(aes(colour=model,linetype=model),lwd=1)+
	geom_ribbon(aes(fill = model), alpha=0.3)+
	labs(x="time (years)",y=expression(mean~transmission~rate~during~asymptomatic~stage~(year^-1))) +
	theme(axis.title.y = element_text(margin = margin(0,10,0,0)),
		axis.title.x = element_text(margin = margin(10,0,0,0)),
		legend.position = "none") +
	facet_wrap(~model, nrow = 2) +
	zero_margin

@@

gg_durtraj <- ggplot(ss3,
                     aes(tvec,mean,ymin=lwr,ymax=upr))+
	geom_line(aes(colour=model,linetype=model),lwd=1)+
	geom_ribbon(aes(fill = model), alpha=0.3)+
	labs(x="time (years)",y=expression(mean~duration~of~asymptomatic~stage~(years))) +
	theme(axis.title.y = element_text(margin = margin(0,10,0,0)),
		axis.title.x = element_text(margin = margin(10,0,0,0)),
		legend.position = "none") +
	facet_wrap(~model, nrow = 2) +
	zero_margin

@@

gg_univ <- ggplot(mLw,aes(value,model,fill=model))+
	geom_violinh(width=1)+
	theme(legend.position = "none") +
	facet_wrap(~variable,scale="free_x")+
	guides(fill=guide_legend(reverse=TRUE))+
	labs(y="")+
	geom_point(data=data.frame(model="random",variable="equilibrium virulence",
                               value=rval),pch=22,size=3,show.legend=FALSE) +
	zero_x_margin
print(gg_univ)

@@

sL$model <- factor(sL$model, c("random","pairform+epc", "pairform", "instswitch+epc","instswitch" , "implicit"))

@@

gg_univ.epi <- ggplot(mLw.epi,aes(value,model,fill=model))+
	geom_violinh(width=1)+
	theme(legend.position = "none") +
	facet_wrap(~variable,scale="free_x")+
	guides(fill=guide_legend(reverse=TRUE))+
	labs(y="")+
	geom_point(data=data.frame(model="random",variable=c("Equilbrium asymptomatic transmission rate",
																											 "Equilibrium duration of asymptomatic stage"),
                               value=c(rval.epi.t, rval.epi.d)),pch=22,size=3,show.legend=FALSE) +
	zero_x_margin
print(gg_univ.epi)

@@

```{r sumtab,as.is=TRUE,eval=FALSE}
rq <- function(x,q,digits=3) {
    round(quantile(x,q),digits)
}
mLtab <- mL.epi %>% group_by(model,variable) %>%
    summarise(lwr=rq(value,0.025),
              med=rq(value,0.5),
              upr=rq(value,0.975)) %>%
    mutate(variable=abbreviate(variable,30)) %>%
    ungroup() %>%
    arrange(variable,model)
kable(mLtab)
```

```{r sumvals,echo=FALSE,eval=FALSE}
ff <- function(model,variable,r=3) {
    mm <- mLtab[mLtab$model==model & mLtab$variable==variable,3:5]
    round(unlist(mm),r)
}
mindur_random <- ff("random","peak_dur",1)
mindur_pfepc <-  ff("pairform+epc","peak_dur",1)
mindur_implicit  <- ff("implicit","peak_dur",1)
maxt_random <- ff("random","peak_t",2)
maxt_pfepc <- ff("pairform+epc","peak_t",2)
maxt_implicit  <- ff("implicit","peak_t",2)
save(list=ls(pattern="^(maxt|mindur)"),file="../ms/maxminstats.RData")
```

```{r fig4_func, echo = FALSE}
trim_gg <- function(gg,hack_spaces=TRUE) {
    n <- gg$nrow
    gg$nrow <- gg$ncol <- n-1
    v <- 1:n^2
    gg$plots <- gg$plots[v>n & v%%n!=0]
    gg$xAxisLabels <- gg$xAxisLabels[-n]
    gg$yAxisLabels <- gg$yAxisLabels[-1]
    ## ggpairs tries to parse labels, so this fails if they
    ## have spaces in them ... maybe there's a better way?
    if (hack_spaces) {
        gg$xAxisLabels <- gsub("_"," ",gg$xAxisLabels)
        gg$yAxisLabels <- gsub("_"," ",gg$yAxisLabels)
    }
    return(gg)
}
